Predicting the spread and persistence of genetically modified dominant sterile male mosquitoes

### 2021-02-05 inst/manuscript/Draft/bmc_article_v10.tex
2nd response to TM comments
Wordsmithed Adrien's 2nd set of responses to TM comments

\section{Results}
\subsection{WT parameters}
Table \ref{tble:sumStatPPpost} provides the summary statistics of the posterior distributions of the PDE model parameters (Figure \ref{fig:prior_posterior} provides both the priors and posteriors for comparison). The use of the MRR data allowed us to provide refined estimates for the parameters of the PDE model. The diffusion coefficient in particular has seen its uncertainty decrease, yielding a mean value of 127 m$^2$ per day. The chemotaxis component has a posterior mean value of about $0.07$, while the range parameter for the mosquito attraction is about $33.9$ m.\\
In the posterior samples, we could identify a high level of correlation between the dispersal and swarm attraction parameters, as can be expected. The shape of this correlation means that high dispersal values correlates with low attraction, and vice-versa. The posterior distribution of dispersal and attraction are also linked to the range of the traps laid out in the field. With limited long range traps, no long range catches were made, limiting the ability of the model to capture possible high dispersal values.

@@

The dispersal of the DSM mosquitoes is balanced by the mortality rate. Because of this, the DSM are not really expected to disperse far from their release site, with the expected number of mosquitoes per cell delineated by the red and orange contours in Figure \ref{fig:plotSpread}. For instance, while the spread is expected to extend on average to up to $500$m away from the release location by day $2$ (there is a probability of $0.99$ or more  of not finding a single mosquito further away), the extent then contracts quickly to a limited area (less than $250$m from release location) by day $5$, to finally about $150$m away from the release location at day $12$.

>>>>

\section{Results}
\subsection{WT parameters}
Table \ref{tble:sumStatPPpost} provides the summary statistics of the posterior distributions of the PDE model parameters (Figure \ref{fig:prior_posterior} provides both the priors and posteriors for comparison). The use of the MRR data allowed us to provide refined estimates for the parameters of the PDE model. The diffusion coefficient in particular has seen its uncertainty decrease, yielding a mean value of 127 m$^2$ per day. The chemotaxis component has a posterior mean value of about $0.07$, while the range parameter for the mosquito attraction is about $33.9$ m.\\

The posterior samples of the dispersal and swarm attraction parameters are highly correlated such that high dispersal values are associated with low attraction, and vice-versa. We anticipated this and deliberately chose a weakly informative prior for the attraction parameter to allow the data to drive their posterior estimates as far as possible. The largest observable dispersal, however, is clearly dictated by the distance between the sources of attractant (compounds) and the traps laid out in the field. In this instance, all traps were laid within 500m of release sites and compounds \citep[Figure 1]{Epopa2017} limiting the ability to infer the possibility of the much higher dispersal values represented in the expert prior (Figure~\ref{fig:prior_posterior}).

@@

The dispersal of the DSM mosquitoes is balanced by the mortality rate. Because of this, the DSM are not expected to disperse far from their release site, with the expected number of mosquitoes per cell delineated by the red and orange contours in Figure \ref{fig:plotSpread}. For instance, while the spread is expected to extend on average to up to $500$m away from the release location by day $2$ (with at most a 1\% chance of finding a mosquito further away), the extent then contracts quickly to a limited area (less than $250$m from release location) by day $5$, to finally about $150$m away from the release location at day $12$.
